This literature review provides a comprehensive understanding of the MEVN stack, Docker, their benefits, and best practices. It forms the basis for the design and development of the e-commerce application for a sports equipment shop website.
\section{Web technology stacks}
A technology stack, often referred to as a solutions stack or a data ecosystem, is a list or combination of programming languages, tools, and technologies that are used to build and run a web application. Each layer of the technology stack builds on the foundation that's been laid by the layer below it.

Choosing the right technology stack is crucial for project success. The technology stack not only affects the speed and timeline of the project but also influences the ability to scale and the overall cost. Some common technology stacks include LAMP (Linux, Apache, MySQL, PHP), MEAN (MongoDB, Express.js, AngularJS, Node.js), and MEVN (MongoDB, Express.js, Vue.js, Node.js).
\section{MEVN}
\subsection{Overview of MEVN stacks}
The \textbf{MEVN} stack is a popular JavaScript software stack used to build powerful web applications. It consists of four different technologies: MongoDB, Express.js, Vue.js, and Node.js.
\begin{itemize}
    \item[-] \textbf{MongoDB:} A highly scalable and flexible document database with efficient querying and indexing. MongoDB stores data in flexible, JSON-like documents, meaning fields can vary from document to document and data structure can be changed over time.
    \item[-] \textbf{Express.js:} A minimal and flexible Node.js web application framework that provides robust features for web and mobile applications. It provides a myriad of HTTP utility methods and middleware at your disposal, which makes creating a robust API quick and easy.
    \item[-] \textbf{Vue.js:} A progressive JavaScript framework for building user interfaces. It is approachable, performant, and versatile in building single-page web applications. VueJS focuses on the view layer. It has a very easy learning curve with a simple API which makes it one of the most loved frameworks.
    \item[-] \textbf{Node.js:} An open-source runtime environment and library used to run web applications outside the client's browser. It is mainly used for server-side programming. It is asynchronous, event-driven, and highly scalable to write servers and databases.
\end{itemize}

\subsection{Benefits of the MEVN Stack}
The \textbf{MEVN} stack provides multiple advantages:
\begin{itemize}
    \item[-] \textbf{Platform Independence:} The MEVN stack is platform-independent, which means it can be used across different operating systems.
    \item[-] \textbf{Single Language Development:} JavaScript is used on all levels of development from client-side to server-side which simplifies the process and makes development faster and efficient.
    \item[-] \textbf{MVC Architecture:} The MVC (Model-View-Controller) architecture in the back-end organizes the server-side, making back-end development faster and more efficient.
    \item[-] \textbf{Easy Learning Curve:} Vue.js is known for its easy learning curve and simple API, which makes it a popular choice among developers.
\end{itemize}
In the context of this project, the MEVN stack's benefits lie in its ability to create a scalable, robust, and efficient e-commerce application for a sports equipment shop website.

\subsection{Challenges of the MEVN Stack}
Despite its benefits, the  \textbf{MEVN} stack does have some challenges:
\begin{itemize}
    \item[-] \textbf{New Framework:} Vue.js is a relatively new framework and doesn't have the support of a large community compared to other frameworks like React or Angular.
    \item[-] \textbf{Lack of Plugins:} Due to its novelty, Vue.js lacks the extensive range of plugins available to older, more established frameworks.
    \item[-] \textbf{Imperfect Core Functionality:} Developers may face difficulties due to its imperfect core functionality since it is not a full-fledged framework. Therefore, developers have to depend on third-party services.
\end{itemize}
In the context of this project, the MEVN stack's benefits lie in its ability to create a scalable, robust, and efficient e-commerce application for a sports equipment shop website.
\subsection{Docker and Containerization}

\textbf{Docker} is an open-source platform that automates the deployment, scaling, and management of applications using containerization.
\begin{itemize}
    \item[-] A \textbf{Docker} container is a standalone, executable package that includes everything needed to run an application, including the code, runtime, libraries, environment variables, and config files.
    \item[-] \textbf{Docker} can be used to run MongoDB in an isolated environment, without the need for a dedicated server. This simplifies the setup process, ensures that the database runs in a consistent environment, and makes it easier to migrate to different servers.

\end{itemize}